---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `baystability`: Bayesian Stability Analysis of Genotype by Environment Interaction (GEI)


###### Version : [`r getNamespaceVersion("baystability")`](https://myaseen208.com/baystability/); Copyright (C) 2018-2024: License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)


##### *Muhammad Yaseen^1,2^, Diego Jarquin^3^, Sergio Perez-Elizalde^4^,  Juan Burgueño^5^, Jose Crossa^6,7,8,9^*
  

1. School of Mathematical & Statistical Sciences, Clemson University, Clemson, South Carolina, USA
2. Department of Mathematics & Statistics, University of Agriculture Faisalabad, Pakistan
3. Agronomy Department, University of Florida, Gainesville, FL, United States
4. Colegio de Postgraduados, Montecillo,Estado de México 56230, México
5. Consultative Group on International Agricultural Research: CGIAR
6. Department of Statistics and Operations Research, and Distinguish Scientist Fellowship Program, King Saud University, Riyah, Saudi Arabia
7. AgCenter, Louisiana State University, Baton Rouge, Louisiana, USA
8. Colegio de Postgraduados, Montecillos, Mexico
9. International Maize and Wheat Improvement Center (CIMMYT), Mexico-Veracruz, Mexico 

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/baystability)](https://cran.r-project.org/package=baystability)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/baystability?color=green)](https://CRAN.R-project.org/package=baystability)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/baystability) -->

```{r, results='asis', echo=FALSE}
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("baystability")) != "",
               yes = getNamespaceVersion("baystability"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/baystability", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/baystability", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/baystability)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/baystability/total.svg)] -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/baystability)
***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("baystability", fields = "Description")))`

## Installation
The package can be installed from CRAN as follows:

```{r, eval=FALSE}
install.packages("baystability", dependencies = TRUE)
```



The development version can be installed from github as follows:

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("myaseen208/baystability")
```



## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package = "baystability")
```

## Links

[CRAN page](https://cran.r-project.org/package=baystability)

[Github page](https://github.com/myaseen208/baystability)

[Documentation website](https://myaseen208.com/baystability/)



## Citing `baystability`
To cite the methods in the package use:


```{r, comment = ""}
citation("baystability")
```
